Contention management for Cloud RAN over an optical ring

### 2018-02-20 Papier NGreen/article.tex
petites typos

\usepackage{xspace}
\usepackage{graphicx,graphics} 
\usepackage{hyperref} 
\usepackage{mathtools, bm}
\usepackage{caption}
\usepackage{amssymb, bm}
\usepackage{complexity}
\usepackage{amsthm}
%\usepackage{authblk}
\usepackage{color}
\usepackage{amsmath}

@@

\newcommand{\todo}[1]{{\color{red} TODO: {#1}}}	
\newtheorem{prop}{Proposition}

@@

\address{\addressmark{1}David Laboratory, UVSQ \\
  \addressmark{2}BNokia Bell Labs France}
\keywords{Optical ring, Latency, C-RAN, SDN}

@@

\section{Introduction}

@@

   \section{Performance evaluation of the N-GREEN optical ring}
   \label{sec:oportmethods}
  One first study the latency of the C-RAN and BE traffics when the ring follows an opportunistic insertion policy: when a node wants to send some data, it uses the first free container available on the ring. If a node can not send a container, because there is no free slots or several containers must be send at the same time, the containers surplus are buffered in an insertion buffer.
  Two different method to manage this insertion buffer are proposed here. The FIFO rule is compared to another method that uses two insertion buffers: one for the containers with BE, and another for the containers with C-RAN. If there is a free container on the ring, the node wants to empty the insertion buffer with C-RAN containers first.
  Fig~\ref{fig:resultopport} gives the cumulative distribution of both C-RAN and BE traffics latencies for the FIFO rule or the C-RAN first rule. On this experiment, the offsets of the RRH are randomly drawn in the period. The parameters of the ring are given by fig~\ref{fig:params}. Those results are computed over $100$ instances of optical rings that have ran during $10,000,000$ unit of time.

>>>>

\usepackage{xspace}
\usepackage{graphicx,graphics} 
\usepackage{mathtools, bm}
\usepackage{caption}
\usepackage{amssymb, bm}
\usepackage{complexity}
\usepackage{amsthm}
%\usepackage{authblk}
\usepackage{color}
\usepackage{amsmath}
\usepackage[colorlinks=true,breaklinks=true,linkcolor=blue]{hyperref}

@@

\newcommand{\todo}[1]{{\color{red} TODO: {#1}}}	
\newtheorem{prop}{Proposition}
\renewcommand{\thefootnote}{\*}

@@

\address{\addressmark{1}David Laboratory, UVSQ \\
  \addressmark{2}Nokia Bell Labs France}
\keywords{Optical ring, Latency, C-RAN, SDN}

@@

\section{Introduction}
 \footnote{ This work was developed around the ANR N-GREEN project. The authors thanks all the Nokia Bell Labs team for their collaboration.}

@@

   \section{Performance evaluation of the N-GREEN optical ring}
   \label{sec:oportmethods}
  One first study the latency of the C-RAN and BE traffics when the ring follows an opportunistic insertion policy: when a node wants to send some data, it uses the first free container available on the ring. If a node can not send a container, because there is no free slots or several containers must be send at the same time, the containers surplus are buffered in an insertion buffer.
  Two different method to manage this insertion buffer are proposed here. The FIFO rule is compared to another method that uses two insertion buffers: one for the containers with BE, and another for the containers with C-RAN. If there is a free container on the ring, the node wants to empty the insertion buffer with C-RAN containers first.
  Fig.~\ref{fig:resultopport} gives the cumulative distribution of both C-RAN and BE traffics latencies for the FIFO rule or the C-RAN first rule. On this experiment, the offsets of the RRH are randomly drawn in the period. The parameters of the ring are given by Fig.~\ref{fig:params}. Those results are computed over $100$ instances of optical rings that have ran during $10,000,000$ unit of time.
